Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-03-02 scripts/04_downstream_analysis.Rmd
ENH more text on the downstream analysis part of the manuscript

```{r go_term_enrichment}

```

>>>>

To find GO terms, we use `biomaRt` to find the mapping between GO terms and
gene mapping. The GO enrichment library `topGO` expects the GO term to gene
mapping to be a list where each item is a mapping between a gene name and a GO
term ID vector.

```text
$NM_199153
[1] "GO:0016020" "GO:0016021" "GO:0007186" "GO:0004930" "GO:0007165"
[6] "GO:0050896" "GO:0050909"

$NM_201361
 [1] "GO:0016020" "GO:0016021" "GO:0003674" "GO:0008150" "GO:0005794"
 [6] "GO:0005829" "GO:0005737" "GO:0005856" "GO:0005874" "GO:0005739"
[11] "GO:0005819" "GO:0000922" "GO:0072686"
```

`biomaRt` queries results a matrix with two named columns of gene names and GO
term ID. **FIXME** matrix or data.frame??

```{r go_to_gene_mapping, results="hide", message=FALSE}
# FIXME move this to the package
source("GO_terms_analysis.R")
genes = getBM(attributes=c("go_id", "refseq_mrna"),
	      values=gene_names,
	      filters="refseq_mrna",
	      mart=ensembl)

# Create gene to GO id mapping
gene_id_go_mapping = create_go_term_mapping(genes)
```

Once the gene ID to GO mapping list is created, `moanin` provides a simple
interface to `topGO` to fetch enriched GO terms.

```{r go_term_enrichment, results="hide", message=FALSE}

cluster = c(3)
ontologies = c("BP", "NF", "CC")
# It's taking too long to compile with everything. Just limit ourselves for
# now to BP
ontologies = c("BP")
all_go_terms = data.frame()
for(cluster in clusters){
    for(ontology in c("BP", "NF", "CC")){ 
	scores = as.numeric(labels == cluster)
	names(scores) = gene_names
	go_terms_enriched = find_enriched_go_terms(
	    scores,
	    gene_id_go_mapping)

	if((dim(all_go_terms)[1] == 0) & (dim(go_terms_enriched)[1] != 0)){
	    go_terms_enriched["Cluster"] = cluster
	    go_terms_enriched["Ontology"] = ontology
	    all_go_terms = go_terms_enriched
	}else if(dim(go_terms_enriched)[1] != 0){
	    go_terms_enriched["Cluster"] = cluster
	    go_terms_enriched["Ontology"] = ontology
	    all_go_terms = merge(all_go_terms, go_terms_enriched, all=TRUE)
	}
    }
}
```

```{r echo=FALSE}
library(kableExtra)

all_go_terms = all_go_terms[
    order(all_go_terms[, "Cluster"],
	  all_go_terms[, "resultFisher_padj"]), ]

kable(all_go_terms, "html", escape=F, digits=4) %>%
    kable_styling("striped", full_width=TRUE) 
```
